\clearpage
\theendnotes

\clearpage
\begin{thebibliography}{1\kern\bibindent}

\bibitem{ACDIS2016} ACDIS. 2016. ``Nuclear South Asia: A Timeline, The Program Arms Control {\&} Domestic and International Security." Accessed August. \url{http://acdis.illinois.edu/resources/arms-control-quick-facts/timeline-for-nuclear-south-asia}.

\bibitem{Barrat2004} Barrat A., M. Barthelemy, R. Pastor-Satorras, and A. Vespignani. 2004. ``The Architecture of Complex Weighted Networks." \textit{Proceedings of the National Academy of Sciences of the United States of America} 101 (11): 3747--3752.

\bibitem{Cirincione2005} Cirincione, Joseph, Jon Wolfsthal, and Miriam Rajkumar. 2005. \textit{Deadly Arsenals: Nuclear, Chemical, and Biological Threats}. Washington, D.C.: Carnegie Endowment for International Peace.

\bibitem{Coles2001} Coles, Stuart. 2001. \textit{An Introduction to Statistical Modeling of Extreme Values}. London: Springer.

\bibitem{Edgell1984}  Edgell, Stephen E., and Sheila M. Noon. 1984. ``Effect of Violation of Normality on the $t$ Test of the Correlation Coefficient." \textit{Psychological Bulletin} 95 (3): 576--583.

\bibitem{Fuhrmann2009} Fuhrmann, Matthew. 2009. ``Taking a Walk on the Supply Side: the Determinants of Civilian Nuclear Cooperation." \textit{Journal of Conflict Resolution} 53 (2): 181--208.

\bibitem{Fuhrmann2014} Fuhrmann, Matthew, and Todd S. Sechser. 2014. ``Nuclear Strategy, Nonproliferation, and the Causes of Foreign Nuclear Deployments." \textit{Journal of Conflict Resolution} 58 (3): 455--480.

\bibitem{Gartzke2014} Gartzke, Erik, Jeffrey M. Kaplow, and Rupal N. Mehta. 2014. ``The Determinants of Nuclear Force Structure." \textit{Journal of Conflict Resolution} 58 (3): 481--508.

\bibitem{Goldblat2004} Goldblat, Jozef. 2004. ``Nuclear-Weapon-Free-Zone Treaties: Benefits and Deficiencies." In \textit{Building a Weapons of Mass Destruction Free Zone in the Middle East: Global Non-Proliferation Regimes and Regional Experiences,} edited by UNIDIR, 53--75. Geneva: United Nations.

\bibitem{Gopalan1992} Gopalan, Sita. 1992. ``India's China Policy." \textit{Strategic Analysis} 14 (12): 1401-1414.

\bibitem{Hymans2008} Hymans, Jacques E.C. 2008. ``Assessing North Korean Nuclear Intentions and Capacities: A New Approach." \textit{Journal of East Asian Studies} 8: 259--292.

\bibitem{Hymans2010} ---. 2010. ``When Does a State Become a `Nuclear Weapon State'?" \textit{Nonproliferation Review} 17 (1): 161--180. 

\bibitem{IAEA2015a} IAEA. 2015a. ``Integrated Nuclear Fuel Cycle Information Systems." Accessed September. \url{http://infcis.iaea.org/}.

\bibitem{IAEA2015b} ---. 2015b. ``Research Reactor Database." Accessed September. \url{http://nucleus.iaea.org/RRDB/RR/ReactorSearch.aspx?rf=1}.

\bibitem{Jo2007} Jo, Dong-Joon, and Erik Gartzke. 2007. ``Determinants of Nuclear Weapons Proliferation." \textit{Journal of Conflict Resolution} 51 (1): 167--194.

\bibitem{Jones1996} Jones, Daniel M., Stuart A. Bremer, and J. David Singer. 1996. ``Militarized Interstate Disputes, 1816-1992: Rationale, Coding Rules, and Empirical Patterns." \textit{Conflict Management and Peace Science} 15 (2): 163--215.

\bibitem{Keeley2003} Keeley, James F. 2003. \textit{A List of Bilateral Civilian Nuclear Cooperation Agreements}. Calgary, Alberta, Canada: University of Calgary.

\bibitem{Kristensen2013} Kristensen, Hans M., and Robert S. Norris. 2013. ``Global Nuclear Weapons Inventories, 1945-2013." \textit{Bulletin of Atomic Scientists} 69 (5): 78-81.

\bibitem{Kroenig2009} Kroenig, Matthew. 2009. ``Importing the Bomb: Sensitive Nuclear Assistance and Nuclear Proliferation." \textit{Journal of Conflict Resolution} 53 (2): 161--180.

\bibitem{Leeds2002} Leeds, Brett, Jeffrey Ritter, Sara Mitchell, and Andrew Long. 2002. ``Alliance Treaty Obligations and Provisions, 1815-1944." \textit{International Interactions} 28 (3): 237--260.

\bibitem{Lupu2012} Lupu, Yonatan, and Vincent A. Traag. 2012. ``Trading Communities, the Networked Structure of International Relations, and the Kantian Peace." \textit{Journal of Conflict Resolution} 57 (6): 1011--1042.

\bibitem{Maoz2009} Maoz, Zeev. 2009. ``The Effects of Strategic and Economic Interdependence on International Conflict Across Levels of Analysis." \textit{American Journal of Political Science} 53 (1): 223--240.

\bibitem{Montgomery2009} Montgomery, Alexander H., and Scott D. Sagan. 2009. ``The Perils of Predicting Proliferation." \textit{Journal of Conflict Resolution} 53 (2): 302--328.

\bibitem{Morone2015} Morone, Flaviano, and Hern\'{a}n A. Makse. 2015. ``Influence Maximization in Complex Networks through Optimal Percolation." \textit{Nature} 524 (7563): 65--68.

\bibitem{Nicosia2015} Nicosia, Vincenzo, and Vito Latora. 2015. ``Measuring and Modeling Correlations in Multiplex Networks." \textit{Physical Review E} 92 (3): 032805--032825.

\bibitem{Oneal1997} Oneal, John R., and Bruce Russett. 1997. ``The Classical Liberals Were Right: Democracy, Interdependence, and Conflict, 1950-1985." \textit{International Studies Quarterly} 42 (2): 267--293.

\bibitem{Oneal1999a} ---. 1999a. ``Assessing the Liberal Peace with Alternative Specifications: Trade Still Reduces Conflict." \textit{Journal of Peace Research} 36 (4): 423-442.

\bibitem{Oneal1999b} ---. 1999b. ``The Kantian Peace: The Pacific Benefits of Democracy, Interdependence, and International Organization, 1885-1992." \textit{World Politics} 52 (1): 1-37. 

\bibitem{Opsahl2010} Opsahl, Tore, Filip Agneeseens, and John Skvoretz. 2010. ``Node Centrality in Weighted Networks: Generalizing Degree and Shortest Paths." \textit{Social Networks} 32 (3): 245--251.

\bibitem{Pearson1929} Pearson, E. S. 1929. ``Notes on Sampling Tests with Two Variables." \textit{Biometrika} 21 (1/4): 337--360.

\bibitem{Pearson1931} Pearson, Egon S. 1931. ``The Test of Significance for the Correlation Coefficient." \textit{Journal of the American Statistical Association} 26 (174): 128--134.

\bibitem{Reed2010} Reed, Thomas C., and Danny B. Stillman. 2010. \textit{Nuclear Express: A Political History of the Bomb and Its Proliferation}. Minneapolis: Zenith Press.

\bibitem{Russett2001} Russett, Bruce, and John Oneal. 2001. \textit{Triangulating Peace: Democracy, Interdependence, and International Organizations}. New York: Norton.

\bibitem{Sagan1996} Sagan, Scott D. 1996. ``Why Do States Build Nuclear Weapons?: Three Models in Search of a Bomb." \textit{International Security} 21 (3): 54--86.

\bibitem{Singer1972} Singer, J. David, Stuart Bremer, and John Stuckey. 1972. ``Capability Distribution, Uncertainty, and Major Power War, 1820-1965." In \textit{Peace, War, and Numbers}, edited by Bruce Russett, 19--48. Beverly Hills: Sage.

\bibitem{Singh2004} Singh, Sonali, and Christopher R. Way. 2004. ``The Correlates of Nuclear Proliferation: a Quantitative Test." \textit{Journal of Conflict Resolution} 48 (6): 859--885.

\bibitem{Stumpf1995} Stumpf, Waldo. 1995. ``South Africa's Nuclear Weapons Program: From Deterrence to Dismantlement." \textit{Arms Control Today} 25 (10): 3--8.

\bibitem{Sweeney2015} Sweeney, David J., and James Kornell. 2015. ``Network Science Analysis for Nonproliferation Likelihood." Paper presented at the annual meeting for the Institute of Nuclear Materials Management, Indian Wells, California, July 12-16.

\bibitem{Tertrais2011} Tertrais, Bruno. 2011. ``Security Guarantees and Nuclear Non-Proliferation." \textit{Fondation pour la Recherche Strat\'{e}gique}. 

\bibitem{WNA 2015} WNA. 2015. ``Reactor Database." Accessed October. \url{http://world-nuclear.org/NuclearDatabase/Default.aspx?id=27232}.

\end{thebibliography}
